Analysis

### 2022-05-26 EDA_CTCFBSDB.Rmd
work on EDA_CTCFBSDB.Rmd

# Input files
# Predicted data
fileNameIn1 <- file.path(dir_data, "data/allcomp.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/allcomp.txt.gz", fileNameIn1)
# Experimental data
fileNameIn2 <- file.path(dir_data, "data/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz", fileNameIn2)
```

@@

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = mtx_to_gr(mtx = mtx_human, genome_id = "hg19"), file = fileNameOut1)
save(list = mtx_to_gr(mtx = mtx_mouse, genome_id = "mm9"), file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
```

@@

```{r data}
# Read in data
mtx <- read_tsv(fileNameIn2)
```

@@

```{r}
# head(mtx, n = 100) %>% View()
colnames(mtx)
table(mtx$Species)
table(mtx$Build)
mtx$Build[mtx$Build == "galgal3"] <- "galGal3"
table(mtx$ValidationStatus)
table(mtx$CellType)
table(mtx$Occupancy)
summary(mtx$CTCF_Rank %>% as.numeric())
summary(mtx$Readcount %>% as.numeric())
table(mtx$ENCODE)
summary(mtx$ENCODE_Peak)
table(mtx$M1M2_class)
```

@@

```{r}
mtx_to_gr <- function(mtx = mtx, org = "Rhesus") {
  mtx_selected <- mtx[mtx$Species == org, ]
  gr <- GRanges(seqnames = mtx_selected$Chr, IRanges(start = mtx_selected$GenomeBeginLoc, end = mtx_selected$GenomeEndLoc))

@@

organisms <- unique(mtx$Species)
organisms <- organisms[organisms != c("Rhesus")]
for(i in organisms) {
  print(i)
  gr <- mtx_to_gr(mtx, org = i)
  # Output files
  fileNameOut1 <- file.path(dir_data, paste0("results/CTCF_", i, "_CTCFBSDB_experimental.RData"))
  # Save as RData object. 
  # save(list = mtx_to_gr(mtx = mtx_human, genome_id = "hg19"), file = fileNameOut1)
}

# load(file = paste0(subdir, ".RData"))
```

>>>>

# Input files
# Predicted data
fileNameIn1 <- file.path(dir_data, "data/allcomp.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/allcomp.txt.gz", fileNameIn1)
# Experimental data
fileNameIn2 <- file.path(dir_data, "data/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_predicted_human.RData")
fileNameOut1.1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_predicted_human.bed")
fileNameOut2 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_predicted_mouse.RData")
fileNameOut2.1 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_predicted_mouse.bed")
# fileNameOut3 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.RData")
# fileNameOut3.1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.bed")
# fileNameOut4 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.RData")
# fileNameOut4.1 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.bed")
```

@@

hg19.CTCFBSDB.CTCF_predicted_human <- mtx_to_gr(mtx = mtx_human, genome_id = "hg38")
length(hg19.CTCFBSDB.CTCF_predicted_human)
summary(width(hg19.CTCFBSDB.CTCF_predicted_human))
mm9.CTCFBSDB.CTCF_predicted_mouse <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10")
length(mm9.CTCFBSDB.CTCF_predicted_mouse)
summary(width(mm9.CTCFBSDB.CTCF_predicted_mouse))

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg19.CTCFBSDB.CTCF_predicted_human, file = fileNameOut1)
save(list = mm9.CTCFBSDB.CTCF_predicted_mouse, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg19.CTCFBSDB.CTCF_predicted_human, fileNameOut1.1)
export.bed(mm9.CTCFBSDB.CTCF_predicted_mouse, fileNameOut2.1)
```

@@

```{r eval=FALSE}
# Read in data
mtx <- read_tsv(fileNameIn2)
```

@@

```{r eval=FALSE}
# head(mtx, n = 100) %>% View()
colnames(mtx)
table(mtx$Species)
table(mtx$Build)
mtx$Build[mtx$Build == "galgal3"] <- "galGal3"
table(mtx$ValidationStatus)
table(mtx$CellType)
table(mtx$Occupancy)
summary(mtx$CTCF_Rank %>% as.numeric())
summary(mtx$Readcount %>% as.numeric())
table(mtx$ENCODE)
summary(mtx$ENCODE_Peak)
table(mtx$M1M2_class)
```

@@

```{r eval=FALSE}
mtx_to_gr <- function(mtx = mtx, org = "Rhesus") {
  mtx_selected <- mtx[mtx$Species == org, ]
  gr <- GRanges(seqnames = mtx_selected$Chr, IRanges(start = mtx_selected$GenomeBeginLoc, end = mtx_selected$GenomeEndLoc))

@@

organisms <- unique(mtx$Species)
# organisms <- organisms[organisms != c("Rhesus")]
# for(i in organisms) {
#   print(i)
#   gr <- mtx_to_gr(mtx, org = i)
#   # Output files
#   fileNameOut1 <- file.path(dir_data, paste0("results/CTCF_", i, "_CTCFBSDB_experimental.RData"))
#   # Save as RData object. 
#   # save(list = mtx_to_gr(mtx = mtx_human, genome_id = "hg19"), file = fileNameOut1)
# }

# load(file = paste0(subdir, ".RData"))

hg18.CTCFBSDB.CTCF_experimental_human <- mtx_to_gr(mtx = mtx, org = "Human")
length(hg18.CTCFBSDB.CTCF_experimental_human)
summary(width(hg18.CTCFBSDB.CTCF_experimental_human))
```
